Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-25 doc/paper.Rmd
figures 9 and 10

```{r type2, fig.height = 3, fig.width = 4.5, out.width='0.6\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
if (!file.exists("../data/cvcs2.RDS")) {
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
cvcs2$method <- "CS2"
saveRDS(cvcs2, file = "../data/cvcs2.RDS")
} else cvcs2 <- readRDS("../data/cvcs2.RDS")

@@

```{r roc, fig.height = 3.25, fig.width = 4.75, out.width='0.6\\textwidth', fig.cap="ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$. Optimal ROC curves are reached at optimization windows of size 150 and higher. Points of equal error rates (EERs) can be found at the intersection of the dotted line and the ROC curves."}

cvcs %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv), linetype=method)) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~wv, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")

@@

```{r type1, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate."}
errorsCV %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = actual, colour=factor(alpha))) + 
  geom_hline(aes(yintercept=alpha), colour="grey30", size=.5) +
  geom_point(aes(shape=factor(wv)), size=2.5) +
  #  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), size=.8, se=FALSE, method="lm", alpha=.9) +
  theme_bw() +
#  scale_y_log10(breaks=c(0.001,.005, 0.01, 0.05)) +
  scale_shape_discrete(expression("Size of validation window "~w[v])) +
  ylab("Observed type I error rate") +
  xlab(expression("Window size for optimization, "~w[o])) +
  scale_colour_brewer(expression("Nominal type I error "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller="label_both", scales="free") +
  theme(legend.position="bottom")

>>>>

```{r type2, fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
if (!file.exists("../data/cvcs2.RDS")) {
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
cvcs2$method <- "CS2"
saveRDS(cvcs2, file = "../data/cvcs2.RDS")
} else cvcs2 <- readRDS("../data/cvcs2.RDS")

@@

```{r roc, fig.height = 3.25, fig.width = 8, out.width='\\textwidth', fig.cap="ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$. Optimal ROC curves are reached at optimization windows of size 150 and higher. Points of equal error rates (EERs) can be found at the intersection of the dotted line and the ROC curves."}

cvcs %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv), linetype=method)) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_shape_discrete("Method", expression("Validation\nwindow size"~w[v])) +
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~wv, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)") +
  guides(
   colour = guide_legend(order = 3, ncol=2),
   linetype = guide_legend(order = 1, ncol=2),
   shape = guide_legend(order = 2, ncol=2)
 )

@@

```{r type1, fig.width=7.75, fig.height=5.25, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate."}
errorsCV$wv.method <- paste(errorsCV$method, errorsCV$wv, sep=" / ")
errorsCV %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = actual, colour=factor(alpha), 
             linetype=method)) + 
  geom_hline(aes(yintercept=alpha), colour="grey30", size=.5) +
  geom_point(aes(shape=factor(wv.method)), size=2.5) +
  geom_smooth(aes(group=factor(method)), 
              size=.8, se=FALSE, method="lm", alpha=.9) +
  theme_bw() +
  ylab("Observed type I error rate") +
  xlab(expression("Window size for optimization, "~w[o])) +
  scale_colour_brewer(
    expression("Nominal type I error "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller="label_both", scales="free") +
  theme(legend.position="bottom") +
  scale_shape_manual(expression("Method / Size of validation window "~w[v]), values=c(1,16,17)) +
  scale_linetype_manual("Method", values=c(3,1), guide=FALSE) +
  guides(shape = guide_legend(ncol=2),
       #  linetype = guide_legend(ncol=1),
         col = guide_legend(ncol=2))
